Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-07 paper.tex
todos

\textcolor{red}{TODO: focus on the experience we accumulated (general remark).}

@@

\textcolor{red}{TODO: rewrite + describe Scorer API}

The aforementioned \texttt{Pipeline} object
can be passed as an argument to a model selection algorithm.
Available algorithms at the time of writing include random search
\citep{bergstra2012} and ``grid search''.
The latter, which we shall use in this example,
performs an exhaustive search through a grid formed by the Cartesian product
of a set of possible values for each parameter, specified by the user.
In our example, this grid might be given as:

>>>>

\textcolor{red}{TODO: Focus on the experience we accumulated (general remark); motivate our design choices.}

@@

\textcolor{red}{TODO: rewrite and briefly describe the API (see user guide)}\\
\textcolor{red}{TODO: describe Scorer API?}\\
\textcolor{red}{TODO: mention that GridSearchCV objects are themselves estimators}

The aforementioned \texttt{Pipeline} object
can be passed as an argument to a model selection algorithm.
Available algorithms at the time of writing include random search
\citep{bergstra2012} and ``grid search''.
The latter, which we shall use in this example,
performs an exhaustive search through a grid formed by the cartesian product
of a set of possible values for each parameter, specified by the user.
In our example, this grid might be given as:
